The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
fixed typo noted by Emily

Along these lines, the \emph{$F$-pure threshold} %associated to an element of $R$
was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and
%The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
\emph{$F$-threholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.

>>>>

Along these lines, the \emph{$F$-pure threshold} %associated to an element of $R$
was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and
%The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
\emph{$F$-thresholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
